SOL Filamentary transport: update from joint AUG-TCV MST1 experiment

### 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to TeX for itpa

\begin{frame}{Current scan at constant B$_t$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      \includegraphics<4>[width=\textwidth]{NeutralsVsGreenwaldConstantBt}
      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. AUG exhibit a parallel connection length
          which is 5 times smaller then TCV
        \item<2|only@2> AUG: Fueling reduced only at smaller current to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor. 
        \item<4|only@4> Divertor neutral density estimated starting
          from D$_{\alpha}$ calibrated camera and using electron
          density and temperature from LP data. Neutral density
          increase earlier in edge density at smaller current
        \item<5|only@5> Neutrals behavior reconciled whenever
          comparison considered as a function of Greenwald fractin  
        \item<6|only@6> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}  
\end{document}

>>>>

\begin{frame}{Current scan at constant B$_t$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsNe5IpConstantBt}
      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. AUG exhibit a parallel connection length
          which is 5 times smaller then TCV
        \item<2|only@2> AUG: Fueling reduced only at smaller current to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor. 
        \item<4|only@4> Divertor neutral density estimated starting
          from D$_{\alpha}$ calibrated camera and using electron
          density and temperature from LP data. Neutral density
          increases earlier in edge density at lower current
        \item<5|only@5> Neutrals behavior reconciled whenever
          comparison considered as a function of Greenwald fraction  
        \item<6|only@6> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
        \item<7|only@7> Quantifying profile evolution using the
          \alert{shoulder amplitude metric} introduce by Wynn and
          Lipschultz for JET. \alert{Amplitude is the difference
            between normalized upstream density profiles}  
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}  
\end{document}
